Investigation of Limited Detection Schemes for Light Scattering of Optically Trapped Asymmetric Particles

### 2023-03-31 Latex files/Manuscript_submission.tex
Update to Manuscript_submission

@@

Our goal is to determine the orientation of the trapped dimer based on the scattering data $I(\hat{n}, \ \theta_k)$. Rather than aim immediately for an exact estimate of the dimer's orientation, for the purposes of interpretation of the scattering and optimisation of the measurement setup it is more convenient to discretize the possible orientation space  into a number of possible reference orientations, which we can then use as 'classification categories' in a neural network methodology to map scattering data to orientation (see below for further discussion).  Here we choose $\textit{n}_{ref} \ = \ 30$ reference orientations $\hat{\bf n}_{\alpha}$  evenly distributed on a unit sphere \cite{Rey2006} (Figure~\ref{fig:dimer}b) leading to a maximum nearest-neighbour spacing between two neighbouring reference orientations of 0.895 radians. Using MSTM we compute the raw intensities at each of the measurement angles that would be generated by a dimer in each reference orientation, $I(\hat{\bf n}_{\alpha}, \theta_k)$. (Note that if all measurement angles were in the same plane we would obtain identical signals for certain sets of different reference orientations, hence $\theta_4$ projects out of the horizontal plane). The raw intensities are normalized according to:
\begin{align}
\label{eq:scale}
  y_k(\hat{\bf n}_\alpha)
  = 
  \frac{I(\hat{\bf n}_\alpha, \theta_k) - \langle I(\hat{\bf n},\theta_k) \rangle } 
  {\langle I^2(\hat{\bf n},\theta_k) \rangle -\langle I(\hat{\bf n}, \theta_k)\rangle^2}
\end{align}
where the denominator is simply the standard deviation across the set of values $I(\hat{\bf n}, \theta_k)$. The reference orientations, raw intensities, and scaled signals are given in Tables~\ref{tab:A1} and \ref{tab:A2}.

>>>>

\subsection{Brownian Simulation}
\label{sec:brownian}

We use the Brownian OT package developed by Fung~\textit{et~al} \cite{Vigilante2020Brownian_OT} to simulate the motion of an asymmetric dimer (Figure~\ref{fig:dimer}a) within an optical trap. Brownian OT combines MSTM \cite{Mishchenko1996MSTM} and ``Optical Tweezer Toolbox'' (\textit{ott}) \cite{Lenton2020} to simulate the motion of arbitrary
shaped sphere clusters. We simulate the motion of a dimer trapped in a highly focused Gaussian beam by calculating its diffusion tensor according to the analytical solutions provided by Nir and Acrivos \cite{nir_acrivos_1973}. For a dimer of arbitrary sized spheres the diffusion tensor - which describes the Cartesian forces and torques - is a 6 $\times$ 6 matrix:
\begin{align}
	\begin{pmatrix}
		F_x \\ F_y \\ F_z \\ T_x \\ T_y \\ T_z 
	\end{pmatrix}
	= \begin{pmatrix}
	a_1 &   0  &     0     &   0  & d_1 &     0 \\
	 0  &  a_1 &     0     & -d_1 &  0  &     0 \\
	 0  &   0  & a_1 + a_2 &   0  &  0  &     0 \\
	 0  & -d_1 &     0     &  b_1 &  0  &     0 \\
	d_1 &   0  &     0     &   0  & b_1 &     0 \\
	 0  &   0  &     0     &   0  &  0  & b_1 + b_2     
	\end{pmatrix}
	\begin{pmatrix}
		v_{k0} - V_k \\ v_{k0} - V_k \\ v_{k0} - V_k \\
		\omega_x - \Omega_x \\ \omega_y - \Omega_y \\ \omega_z - \Omega_z
	\end{pmatrix}
\end{align}

where each matrix component is scaled by a factor of $k_B T/\pi \eta$ When both sphere's are identically sized - as in Fung~\textit{et. al}'s work - $d_1$ goes to zero; however for our work with asymmetric spheres these components are significant enough to be considered. We simulated a silica dimer ($n = 1.45$) in a suspension of water ($n_{med} = 1.33$) over the course of $10 \ s$ with a simulation time step of $1 \times 10^{-5} \ s$.

@@

Our goal is to determine the orientation of the trapped dimer based on the scattering data $I(\hat{n}, \ \theta_k)$. Rather than aim immediately for an exact estimate of the dimer's orientation, for the purposes of interpretation of the scattering and optimisation of the measurement setup it is more convenient to discretize the possible orientation space into a number of possible reference orientations, which we can then use as 'classification categories' in a neural network methodology to map scattering data to orientation (see below for further discussion).  Here we choose $\textit{n}_{ref} \ = \ 30$ reference orientations $\hat{\bf n}_{\alpha}$  evenly distributed on a unit sphere \cite{Rey2006} (Figure~\ref{fig:dimer}b) leading to a maximum nearest-neighbour spacing between two neighbouring reference orientations of 0.895 radians. Using MSTM we compute the raw intensities at each of the measurement angles that would be generated by a dimer in each reference orientation, $I(\hat{\bf n}_{\alpha}, \theta_k)$. While the number and position of detection fibres is technically arbitrary there are several constraining factors that limit our ability to infer useful information from the trapped object, see Section~\ref{sec:Discussion} for a detailed breakdown of our choice of detection angles. The raw intensities are normalized according to:
\begin{align}
\label{eq:scale}
  y_k(\hat{\bf n}_\alpha)
  = 
  \frac{I(\hat{\bf n}_\alpha, \theta_k) - \langle I(\hat{\bf n},\theta_k) \rangle } 
  {\langle I^2(\hat{\bf n},\theta_k) \rangle -\langle I(\hat{\bf n}, \theta_k)\rangle^2}
\end{align}
where the denominator is simply the standard deviation across the set of values $I(\hat{\bf n}, \theta_k)$. The reference orientations, raw intensities, and scaled signals are given in Tables~\ref{tab:A1} and \ref{tab:A2}.
